Overview

### 2021-05-15 overview_gh.Rmd
Make all vignettes not emitting constant changing information
new ui, fix #26

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
  )
set.seed(42)
```
The validation test is called "oolong test" (for reading tea leaves). Creating oolong test for topic models and dictionary-based uses the same function: `create_oolong()`. The most important parameters are `input_model` and `input_corpus`. Setting each of them to `NULL` generates different tests.

@@

To create an oolong test, use the function `create_oolong_test`.

```{r createtest}
oolong_test <- create_oolong(abstracts_stm)
oolong_test
```

@@

```{r createtest2}
oolong_test <- create_oolong(abstracts_stm, abstracts$text)
oolong_test
```

@@

```{r step1}
oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text)
```

@@

```{r step2}
oolong_test_rater2 <- clone_oolong(oolong_test_rater1)
```

@@

```{r, eval = FALSE}
## Let rater 1 do the test.
oolong_test_rater1$do_word_intrusion_test()
oolong_test_rater1$do_topic_intrusion_test()
oolong_test_rater1$lock()

## Let rater 2 do the test.
oolong_test_rater2$do_word_intrusion_test()
oolong_test_rater2$do_topic_intrusion_test()
oolong_test_rater2$lock()
```

@@

```{r warplda2}
### Just word intrusion test.
oolong_test <- create_oolong(abstracts_warplda)
oolong_test
```

@@

```{r warplda4}
oolong_test <- create_oolong(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm)
oolong_test
```

@@

```{r goldstandard}
oolong_test <- create_oolong(input_corpus = trump2k, construct = "positive")
oolong_test
```

@@

```{r}
trump <- create_oolong(input_corpus = trump2k, exact_n = 40)
trump2 <- clone_oolong(trump)
```

@@

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
  )
set.seed(42)
```
The validation test is called "oolong test" (for reading tea leaves). This package provides several functions for generating different types of oolong test.

| function | purpose                                                                                                                     |
|---------:|:----------------------------------------------------------------------------------------------------------------------------|
|   `wi()` | validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
|   `ti()` | validating a topic model with [topic intrusion test](#topic-intrusion-test)                                                 |
| `witi()` | validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
|   `gs()` | oolong test for [creating gold standard](#creating-gold-standard)                                                           |

All of these tests can also be generated with the function [`create_oolong`](#backward-compatibility). As of version 0.3.20, it is no longer recommended.

@@

To create an oolong test with word intrusion test, use the function `wi`. It is recommended to provide a user id of coder who are going to be doing the test.

```{r createtest}
oolong_test <- wi(abstracts_stm, userid = "Hadley")
oolong_test
```

@@

```{r createtest2}
oolong_test <- ti(abstracts_stm, abstracts$text, userid = "Julia")
oolong_test
```

@@

```{r step1}
oolong_test_rater1 <- witi(abstracts_stm, abstracts$text, userid = "Yihui")
```

@@

```{r step2}
oolong_test_rater2 <- clone_oolong(oolong_test_rater1, userid = "Jenny")
```

@@

```{r, eval = FALSE}
## Let Yihui do the test.
oolong_test_rater1$do_word_intrusion_test()
oolong_test_rater1$do_topic_intrusion_test()
oolong_test_rater1$lock()

## Let Jenny do the test.
oolong_test_rater2$do_word_intrusion_test()
oolong_test_rater2$do_topic_intrusion_test()
oolong_test_rater2$lock()
```

@@

```{r warplda2}
### Just word intrusion test.
oolong_test <- ti(abstracts_warplda, userid = "Lionel")
oolong_test
```

@@

```{r warplda4, , message = FALSE, results = 'hide', warning = FALSE}
oolong_test <- witi(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm, userid = "Mara")
```

```{r warplda5}
oolong_test
```

@@

```{r goldstandard}
oolong_test <- gs(input_corpus = trump2k, construct = "positive", userid = "Joe")
oolong_test
```

@@

```{r}
trump <- gs(input_corpus = trump2k, exact_n = 40, userid = "JJ")
trump2 <- clone_oolong(trump, userid = "Winston")
```

@@

## Backward compatibility

Historically, oolong test objects could only be generated with only one function: `create_oolong`. It is no longer the case and no longer recommended anymore. It is still retained for backward compatibility purposes. If you still need to use  `create_oolong()`, the most important parameters are `input_model` and `input_corpus`. Setting each of them to `NULL` generates different tests.

### 2021-05-15 vig_body.Rmd
Make all vignettes not emitting constant changing information
new ui, fix #26

The validation test is called "oolong test" (for reading tea leaves). Creating oolong test for topic models and dictionary-based uses the same function: `create_oolong()`. The most important parameters are `input_model` and `input_corpus`. Setting each of them to `NULL` generates different tests.

>>>>

The validation test is called "oolong test" (for reading tea leaves). This package provides several functions for generating different types of oolong test.

| function | purpose                                                                                                                     |
|---------:|:----------------------------------------------------------------------------------------------------------------------------|
|   `wi()` | validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
|   `ti()` | validating a topic model with [topic intrusion test](#topic-intrusion-test)                                                 |
| `witi()` | validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
|   `gs()` | oolong test for [creating gold standard](#creating-gold-standard)                                                           |

All of these tests can also be generated with the function [`create_oolong`](#backward-compatibility). As of version 0.3.20, it is no longer recommended.
